Delta Factor - A New Authorization Factor

### 2022-08-11 paper1.tex
pix->table ok
pix->table okay

% New = "Delta Factor" due to line width
\documentclass[a4paper, 11pt]{article} 				%Short reports and scientific journals
% \documentclass{report}							% Books and thesis
\usepackage[utf8]{inputenc}						% 128++ UTF-8 charset -----------------------
\usepackage{graphicx}
\graphicspath{ {/Users/thomasperez/Desktop/finalpix/} }		%abs 
% \graphicspath{{../pdf/}{D:\ImagesforProjectLatex}}

@@

%---------------------------------------------------------------------------------------------------------------------
% Following exactly professor's Canvas example
\section{Abstract}
\setlength{\baselineskip}{1.5\baselineskip}
%This is modus operandi bc as the paper evolves, the abstract changes invariably
\noindent
Man\_In\_The\_Middle-ware, (MITM)[14],[20] is a rapidly growing field of website spoofing that is a challenge for everyone, especially for MITM mitigation and deterrence  developers to keep up with. Many papers have been published that explain the nuances, methods and lengths that the attackers use for "personal gain". According to [1], fairly spectacular results in detecting a MITM attack has been shown. This was accomplished by the group gathering attack data, metrics of the attacks, and analysis for many months, to eventually develop a custom phishing toolkit they named "phoca". That said, the target of our research is two-fold. Firstly, we show improvement in the Stonybrook claim via our novel composite-type methodology using COTP[13].  Secondly, we claim and show that despite Stonybrook's claim, it is possible and provable that application level checks based on easily acccessible and well known network level features along with a secret, can indeed determine with fine granularity, a MITM or !MITM. Ie., an efficient and novel server authentication factor has been developed.

@@

There are methods to avoid and/or determine the existence of a MITM. Traditionally there are eg., Machine Learning methods, ie., the ubiquitous trust-based methods, 2FA, and more new ways, methods, and tools for detection of MITM and more, however they aren't used nor easily available to the general public.
The current status in the field, including the best performing tool is from the basis of our research, with is from the SUNY - Stonybrook paper [1], "Catching Transparent Phish: Analyzing and Detecting MITM  Phishing Toolkits". The name of the extremely efficient tool that they developed is called, "phoca". In brief however, it is discovered that via COTP[13] and of course a shared secret plus a 2FA for security, the APPLICATION layer CAN BE able to help us reveal a MITM if one exists, as opposed to the denial of that concept by Stonybrook, again, knowing that they did a tremendous amount of work on their phoca toolkit.

@@

\noindent
Source Code Available: https://github.com/allesrebel/cotp\\
The organization of the report is as follows:

@@

\subsection{One-Time Passwords}
Earlier web servers only used knowledge to validate or authenticate users. But modern applications employ multi factor approaches to make a more robust authentication method. The most basic of these is the HMAC-based One-Time Password (HOTP)[2][8]. Further factors are introduced, such as time, creating additional constraints on authentication. These methods rely on cryptographic functions that are fast computations in one direction, while computationally complex to reverse.

@@

% Paragraph 2,3,...: introduction of DT techniques ... [Actually - Inspiration]
Inspired by an existing movement, a growing trend towards multi-factor authentication
identified that most methods still only do knowledge-based or device-based validation. This is by incorporating existing and standardized One-Time-Pass code technology, with connection-oriented details (eg., COTP) to produce a method to offer an authentication much stronger than knowledge-based, possession-based, or time-based alone.

@@

\subsection{Results + Data}
\noindent 
Please refer to \textbf{Table-1} below.\\
For the TLS features along, every trial had server and client COTPs match! 
For the TLS + uncorrected TCP features, 2 of 20 trials matched!
For the TLS + corrected TCP features, 16 of 20 trials matched!
Please refer to [6]

\subsubsection{\textbf{Table-1} Round Trip Times}

% \includegraphics[width=\textwidth]{pix3}
\includegraphics[width=5cm]{pix3}

% Due to time constraints, and deprecated examples online, I'l use an Excel png		
% Server RTT ms, Client RTT ms, ABS Diff
% 21	22	1
% 21	25	4

% 18	22	4
% 19	23	4
%19	21	2
% 19	22	3
% 18	23	5
% 21	23	2
% 18	21	3
% 17	20	3
% 19	20	1
% 18	21	3

% 19	23	4
% 19	20	1
% 20	21	1
% 18	21	3
% 18	22	4
% 19	20	1
% 20	24	4
% 19	20	1
% 19	20	1
% 18	21	3

>>>>

% New = "Delta Factor" due to line width
\documentclass[a4paper, 11pt]{article} 				%Short reports and scientific journals
% \documentclass{report}							% Books and thesis
\usepackage[utf8]{inputenc}						% 128++ UTF-8 charset -----------------------
\usepackage{graphicx}
\usepackage{booktabs,siunitx}

\graphicspath{ {/Users/thomasperez/Desktop/finalpix/} }		%abs 
% \graphicspath{{../pdf/}{D:\ImagesforProjectLatex}}

@@

%---------------------------------------------------------------------------------------------------------------------
% Following exactly professor's Canvas example
\section{Abstract}
\setlength{\baselineskip}{1.5\baselineskip}
%This is modus operandi bc as the paper evolves, the abstract changes invariably
\noindent
Man\_In\_The\_Middle-ware, (MITM)[14][15][20] is a rapidly growing field of website spoofing that is a challenge for everyone, especially for MITM mitigation and deterrence  developers to keep up with. Many papers have been published that explain the nuances, methods and lengths that the attackers use for "personal gain". According to [1], fairly spectacular results in detecting a MITM attack has been shown. This was accomplished by the group gathering attack data, metrics of the attacks, and analysis for many months, to eventually develop a custom phishing toolkit they named "phoca". That said, the target of our research is two-fold. Firstly, we show improvement in the Stonybrook claim via our novel composite-type methodology using COTP[13].  Secondly, we claim and show that despite Stonybrook's claim, it is possible and provable that application level checks based on easily acccessible and well known network level features along with a secret, can indeed determine with fine granularity, a MITM or !MITM. Ie., an efficient and novel server authentication factor has been developed.

@@

There are methods to avoid and/or determine the existence of a MITM. Traditionally there are eg., Machine Learning methods, ie., the ubiquitous trust-based methods, 2FA, and more new ways, methods, and tools for detection of MITM and more, however they aren't used nor easily available to the general public.
The current status in the field, including the best performing tool is from the basis of our research, with is from the SUNY - Stonybrook paper [1], "Catching Transparent Phish: Analyzing and Detecting MITM  Phishing Toolkits[20]". The name of the extremely efficient tool that they developed is called, "phoca". In brief however, it is discovered that via COTP[13] and of course a shared secret plus a 2FA for security, the APPLICATION layer CAN BE able to help us reveal a MITM if one exists, as opposed to the denial of that concept by Stonybrook, again, knowing that they did a tremendous amount of work on their phoca toolkit.

@@

\noindent
Source Code Available: https://github.com/allesrebel/cotp\\
https://github.com/TomEphraimPerez/CS5540-final\\
\textbf{Organization} of the report is as follows:

@@

\subsection{One-Time Passwords}
Earlier web servers only used knowledge to validate or authenticate users. But modern applications employ multi factor approaches to make a more robust authentication method. The most basic of these is the [5]HMAC-based One-Time Password (HOTP)[2][8]. Further factors are introduced, such as time, creating additional constraints on authentication. These methods rely on cryptographic functions that are fast computations in one direction, while computationally complex to reverse.

@@

% Paragraph 2,3,...: introduction of DT techniques ... [Actually - Inspiration]
Inspired by an existing movement, a growing trend towards multi-factor authentication
identified that most methods still only do knowledge-based or device-based validation. This is by incorporating existing and standardized One-Time-Pass code technology, with connection-oriented details (eg., COTP[9]) to produce a method to offer an authentication much stronger than knowledge-based, possession-based, or time-based alone.

@@

\subsection{Results + Data}
\noindent 
Please refer to \textbf{Table-1} below.\\
For the TLS features along, every trial had server and client COTPs match! 
For the TLS + uncorrected TCP features, 2 of 20 trials matched!
For the TLS + corrected TCP features, 16 of 20 trials matched!
Please refer to [6]
\subsubsection{\textbf{Table-1} \qquad \qquad Round Trip Times}
% \includegraphics[width=\textwidth]{pix3}							%?
%			\includegraphics[width=5cm]{pix3}					%OK Wed 8-10-22
% ========== TABLE ================ STKOVR
\begin{center}
\begin{tabular}{||c c c ||} 
 \hline
 Col1 & Col2 & Col3 \\ [0.5ex] 
 \hline\hline
 21 & 22 & 1 \\ 				%21 22 1
 \hline
 21 & 25 & 4 \\ 				%21 25 4
 \hline
 18 & 22 & 4 \\ 				%18 22 4
 \hline
 19 & 23 & 4 \\ 				%19 23 4
  \hline
 19 & 21 & 2 \\ 				%19 21 2
  \hline
 19 & 22 & 3 \\ 				%19 22 3
  \hline
 18 & 23 & 5 \\ 				%18 23 5
  \hline
 21 & 23 & 2 \\ 				%21 23 2
  \hline
 18 & 21 & 3 \\ 				%18 21 3
  \hline
 17 & 20 & 3 \\ 				%17 20 3
  \hline
 19 & 20 & 1 \\ 				%19 20 1
  \hline
 18 & 21 & 3 \\ 				%18 21 3
  \hline
 19 & 23 & 4 \\ 				%19 23 4
  \hline
 19 & 20 & 1 \\ 				%19 20 1
  \hline
 20 & 21 & 1 \\ 				%20 21 1
  \hline
 18 & 21 & 3 \\ 				%18 21 3
  \hline
 18 & 22 & 4 \\ 				%18 22 4
  \hline
 19 & 20 & 1 \\ 				%19 20 1
  \hline
 20 & 24 & 4 \\ 			%20 24 4
  \hline
 19 & 20 & 1 \\ 				%19 20 1
  \hline
 19 & 20 & 1 \\ 				%19 20 1
 \hline
 18 & 21 & 3 \\ [1ex]  			%18 21 3
 \hline
\end{tabular}
\end{center}
% == END === TABLE =======================

% Due to time constraints, and deprecated examples online, I'l use an Excel png		
% Server RTT ms, Client RTT ms, ABS Diff
% 21	22	1
% 21	25	4
% 18	22	4
% 19	23	4
% 19	21	2

% 19	22	3
% 18	23	5
% 21	23	2
% 18	21	3
% 17	20	3

% 19	20	1
% 18	21	3
% 19	23	4
% 19	20	1
% 20	21	1

% 18	21	3
% 18	22	4
% 19	20	1
% 20	24	4
% 19	20	1

% 19	20	1
% 18	21	3
